Precision calculations for cosmic shear

### 2017-02-06 limber2.tex
CH: Small changes to make it compile for me Hopefully it also compiles still for you!
limber2.tex:
CH added to the abstract and introduction

\documentclass[useAMS,usenatbib]{mn2e} %
\pdfoutput=1

@@

\title[]
{Precision calculations of the cosmic shear power spectrum projection}

@@

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, first- and
second-order Limber equations for the projection. We show that the spherical
second-order Limber approximation agrees with the full projection at the
percent level for $\ell > 3$. for current surveys. The real-space shear
correlation functions show excellent agreement between all cases. The
consequence for parameter constraints are negligible for current surveys, which
we demonstrate using CFHTLenS data. In particular, the reported tension with
Planck CMB temperature anisotropy results cannot be alleviated. This is in
contrast to the recent claim made by \citet{2016arXiv161104954K}. In the spirit
of reproducible research, our numerical implementation of all approximations
and the full projection are publically available within the package
\texttt{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.

@@

The measurement of weak gravitational lensing by large-scale structures
provides a powerful cosmological probe of dark matter, dark energy, and
modifications to gravity.  As such it is the primary science goal of several
current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large surveys.
Interest in the results from these surveys is high as statistically significant
deviations have been found between the cosmological parameter constraints from
the CMB Planck experiment \citep{2015arXiv150201589P} in comparison to weak
lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{KiDS-450}
and the Canada-France-Hawaii Telescope Lensing Survey
\citep[CFHTLenS;][]{2016arXiv160105786J}.  If the source of this tension is not
a result of so-far unconsidered sources of systematic errors in one or all
experiments, extensions to the standard flat $\Lambda$CDM cosmological models
need to be considered. \citet{joudaki/etal:2017} have shown, for example, that
the tension can be resolved with an evolving dark energy model.

In the era of the upcoming large surveys that will provide measurements of
cosmic shear with unprecedented precision, one needs to revisit the theoretical
model predictions of the observables to make sure that the accuracy of the
models meet the upcoming data. In this paper, we examine the widely used Limber
approximation for the projected weak-lensing power spectrum. We consider
spherical coordinates and the flat-sky approximation, and compute the full
projection as well as first- and second-order Limber approximation. We show
that the latter is an excellent approximation of the full projection. Since it
involves only 1D integrals over the matter power specrum, it is very fast to
calculate numerically and can readily employed in Monte-Carlo sampling methods
to obtain precision constraints on cosmological parameters.

@@

\bibliographystyle{mn2e}
\bibliography{astro}

>>>>

\documentclass[fleqn,usenatbib]{mnras} %
\pdfoutput=1

@@

\title[Precision calculations for cosmic shear]{Precision calculations for cosmic shear}  %??
%{Precision calculations of the cosmic shear power spectrum projection}

@@

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, first- and
second-order Limber equations for the projection. We find that the impact of adopting 
these approximations are negligible when constraining cosmological parameters from 
current weak lensing surveys.
This is demonstrated using data from the Canada-France-Hawaii Lensing Survey (CFHTLenS). 
We find that the reported tension with Planck CMB temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by \citet{2016arXiv161104954K}. 
For future large-scale surveys with unprecedented precision, we show that the spherical
second-order Limber approximation will provide sufficient accuracy, as it is in 
agreement with the full projection at the percent level for $\ell > 3$.  
In the spirit of reproducible research, our numerical implementation of all approximations
and the full projection are publicly available within the package
\texttt{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.

@@

The measurement of weak gravitational lensing by large-scale structures
provides a powerful cosmological probe of dark matter, dark energy, and
modifications to gravity.  As such it is the primary science goal of several
current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.
Interest in the results from these surveys is high as statistically significant
deviations have been found between the cosmological parameter constraints from
the CMB Planck experiment \citep{2015arXiv150201589P} in comparison to weak
lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{KiDS-450}
and the Canada-France-Hawaii Telescope Lensing Survey
\citep[CFHTLenS;][]{2016arXiv160105786J}.  If the source of this tension is not
a result of so-far unconsidered sources of systematic errors in one or all
experiments, extensions to the standard flat $\Lambda$CDM cosmological models
need to be considered. \citet{joudaki/etal:2017} have shown, for example, that
the tension can be resolved with an evolving dark energy model.

In the era of the upcoming large surveys that will provide measurements of
cosmic shear with unprecedented precision, one needs to revisit the theoretical
model predictions of the observables to ensure that the accuracy of the
models meet the upcoming data. In this paper, we examine the widely used Limber
approximation for the projected weak-lensing power spectrum. We consider
spherical coordinates and the flat-sky approximation, and compute the full
projection as well as first- and second-order Limber approximation. We show
that the latter is an excellent approximation of the full projection. Since it
involves only 1D integrals over the matter power spectrum, it is very fast to
calculate numerically and can readily employed in Monte-Carlo sampling methods
to obtain precision constraints on cosmological parameters.

This paper is organised as follows.  In section~\ref{sec:wl} we provide a pedagogical introduction to weak gravitational lensing theory, projections and power spectra for the flat-sky and spherical cases.  In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.  We compare the shear power spectrum and commonly-used two-point shear correlation function for a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.  This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G}.

@@

\bibliographystyle{mnras}
\bibliography{astro}
